\LARGE \bf Energy-Aware Dynamic Mission Planning Algorithm for UAVs

### 2020-10-15 icra-2021.tex
some minor things in the text here and there

Let the mission be a generic continuous twice differentiable TEE $\varphi$ and a set of $\sigma$ tasks $\psi_1,\dots,\psi_{\sigma}$. Moreover, let $t_f$ be the mission final time, $[\,\cdot\,]$ the set $\{1,2,\dots,\,\cdot\,\}$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the upper and lower bound of $\,\cdot\,$.

@@

@@

Equation~(\ref{eq:state-control}) accounts for the energy due to the computations. The energy due to the adjustments is merely a linear combination of the gain factor and the adjustment. Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the energy evolution accordingly. The linearity simulates how a variation affects the energy, for instance, a decrement in the adjustment radius of a circle when the TEE is a circle, adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.

In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy evolution) evolving accordingly to its output (instantaneous energy consumption). Such observation is summarized in the following Lemma.

@@

The plan $\mathcal{M}$ contains a set of ordered lists with $\sigma$ tasks each (recall Definition~\ref{def:mission}). These tasks are simulated by $\sigma$ ROS nodes $\Psi(\mathbf{s}_k):=\left(\psi_1(s_{k,1}),\dots,\psi_\sigma(s_{k,\sigma})\right)$, in fact they input the desired and output the actual computations. Let us define the computations
\begin{equation}\label{eq:qos-def}
  \mathbf{s}_k:=\left\{s_{k,1},\dots ,s_{k,\sigma}\mid \psi_i(s_{k,i})\in\mathbb{S}_{k}\,\forall i\in[\sigma]\right\},
\end{equation}
where $s_{k,i}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $i$-th computation, $\mathbf{s}_k\in\mathbb{S}_k\subseteq\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ computations at time $k$ given $\mathbb{S}_k:=\bigcup_{i\in[\sigma]}{\mathbb{S}_{k,i}}$.

@@

\begin{defn}[Valid mission evolution]\label{def:valid}
  At a generic time instant $k\in[t_f]$ a mission evolution $\mathcal{M}_{k}$ is valid
  \begin{equation}\begin{split}
    \mathbf{u}^a_{k}=\{(\mathbf{c}_{k},\mathbf{s}_{k})\mid&(\varphi(\mathbf{p}_{k-1},\mathbf{c}_{k-1}),\Psi(\mathbf{s_{k-1}}))\in\mathcal{M}_{k-1}\\
    &\Longrightarrow(\varphi(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s}_{k}))\in\mathcal{M}_{k}\}.
  \end{split}\end{equation}
\end{defn}

Note that the controls sequence $\mathbf{u}_k^a$ differs from the control in Equation~(\ref{eq:state-perf}) $\mathbf{u}_k(\mathbf{u}_k^a,\mathbf{u}_{k-1}^a)$. Moreover, the position evolution can be computed directly from Equation~(\ref{eq:pd}). If the velocity is $v\in\mathbb{R}_{\geq 0}$, and the starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.

>>>>

Let the mission be a generic continuous twice differentiable TEE $\varphi$ and a set of $\sigma$ tasks $\psi_1,\dots,\psi_{\sigma}$. Moreover, let $t_f$ be the final time, $[\,\cdot\,]$ the set $\{1,2,\dots,\,\cdot\,\}$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the upper and lower bound of $\,\cdot\,$.

@@

Note that the controls sequence $\mathbf{u}_k^a:=(\mathbf{c}_{k},\mathbf{s}_{k})$--an output of the algorithm--differs from the nominal control in Equation~(\ref{eq:state-perf}) $\mathbf{u}_k(\mathbf{u}_k^a,\mathbf{u}_{k-1}^a)$.

@@

Equation~(\ref{eq:state-control}) accounts for the energy due to the computations. The energy due to the adjustments is merely a linear combination of the gain factor and the adjustment. Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the energy evolution. For instance, a decrement in the adjustment radius of a circle when the TEE is a circle, adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.

In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy evolution) evolving accordingly to its output (instantaneous energy consumption). An observation summarized in the following Lemma.

@@

The plan $\mathcal{M}$ contains a set of ordered lists with $\sigma$ tasks each (recall Definition~\ref{def:mission}). These tasks are simulated by $\sigma$ ROS nodes $\Psi(\mathbf{s}_k):=\left(\psi_1(s_{k,1}),\dots,\psi_\sigma(s_{k,\sigma})\right)$, in fact they input the desired and output the actual computations
\begin{equation}\label{eq:qos-def}
  \mathbf{s}_k:=\left\{s_{k,1},\dots ,s_{k,\sigma}\mid \psi_i(s_{k,i})\in\mathbb{S}_{k}\,\forall i\in[\sigma]\right\},
\end{equation}
where $s_{k,i}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $i$-th computation, $\mathbf{s}_k\in\mathbb{S}_k\subseteq\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ computations at time $k$ given $\mathbb{S}_k:=\bigcup_{i\in[\sigma]}{\mathbb{S}_{k,i}}$.

@@

\begin{defn}[Valid mission evolution]\label{def:valid}
  At a generic time instant $k\in[t_f]$ a mission evolution $\mathcal{M}_{k}$ is valid if its control sequence is valid
  \begin{equation}\begin{split}
    \mathbf{u}^a_{k}=\{(\mathbf{c}_{k},\mathbf{s}_{k})\mid&(\varphi(\mathbf{p}_{k-1},\mathbf{c}_{k-1}),\Psi(\mathbf{s_{k-1}}))\in\mathcal{M}_{k-1}\\
    &\Longrightarrow(\varphi(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s}_{k}))\in\mathcal{M}_{k}\}.
  \end{split}\end{equation}
\end{defn}

Note the position evolution can be computed directly from Equation~(\ref{eq:pd}). If the velocity is $v\in\mathbb{R}_{\geq 0}$, and the starting point $\mathbf{p}_0$, $\mathbf{p}_{k+1}=\mathbf{p}_k\dot{\mathbf{p}}_d(\mathbf{p}_k)/v$.
